%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Nirjharaa Patel} \\ \vspace{1pt}
    Madrid County, Vadodara, Gujarat 391410\\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 9979665587 ~ \href{mailto:nirjharaapatel@gmail@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{nirjharaapatel@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/nirjharaa-patel-b31314221}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn}}  ~
    
    \vspace{-15pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {P P Savani University}{May 2025}
      {B.Tech in Computer Science and Engineering, SGPA: 8.81/10.0 }{
      
   }
       \item {\textbf{Position}: GDSC Executive, Cultural Coordinator}   
    \resumeSubHeadingListEnd
    \vspace{-20pt}

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Object-Oriented Programming
                \item Full Stack Development
                \item Artificial Intelligence
                \item Cloud Computing
                \item Image Processing
                \item Data Science
                \item Internet of Things
                \item Computer Network
                \item Database Management System
                \item Data Structures and Algorithms
                \item Mobile Application Development

                \item Operating System
                \item Software Engineering
            \end{itemize}
        \end{multicols}
        \vspace{-16pt}
        
    %\resumeSubHeadingListEnd
    
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Python, JavaScript, HTML5, CSS3, Java, C, C++, R} \\
     \textbf{Developer Tools(IDEs)}{: Visual Studio Code, MySQL, MongoDB, Eclipse, Netbeans, PyCharm} \\
     \textbf{Technologies/Frameworks}{: GitHub, React.js, Express.js, Node.js, Arduino IDE, Spring MVC}
 \end{itemize}
 \vspace{-23pt}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Digital Dept. - PGP Glass Ltd.(Blackstone Group )}{June 2023}
      {Software Development Intern}{Surat, GJ}
          \resumeItemListStart
            \resumeItem{Established a website using JavaScript, HTML5, and CSS3, that facilitates the chemists to digitally register their Glass Grain Test discoveries, which are utilized further in manufacturing the products at a large scale. }
            \resumeItem{Segregated and simplified the mainframe database which is available for the employees to navigate their way through the supply chain process using SQL and the basics of SAP.}
            \resumeItem{Implemented robust data validation and security measures in the website's backend to ensure the integrity and confidentiality of the Glass Grain Test records. }
       
\resumeItem{Collaborated with the senior software developing team of the company and gained various soft skills: Leadership, Teamwork, Discipline, and Inter-Personal Relationships.}
       
      \resumeItemListEnd

   
    
  \resumeSubHeadingListEnd
\vspace{-22pt}





%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      

        \resumeProjectHeading
          {\textbf{Real-time Chat Application} $|$ \emph{MERN, Socket.IO, ChatEngine.io}}{Jan 2023}
          \resumeItemListStart
            \resumeItem{Designed and implemented a dynamic real-time chat application using the MERN stack (MongoDB, Express, React, Node.js), incorporating Socket.IO for seamless, bidirectional communication and Postman for backend testing. }
            \resumeItem{Applied Tailwind CSS for layout optimization and DaisyUI for user interface components, delivering an aesthetically pleasing and responsive user experience. }
            \resumeItem{Recreated the chat application leveraging ChatEngine.io with React and Node.js }
           \resumeItemListEnd 
          \vspace{-20pt}
         
 \resumeProjectHeading
          {\textbf{Portfolio Website} $|$ \emph{HTML5, CSS3, Javascript}}{Feb 2024}
          \resumeItemListStart
            \resumeItem{Developed a personal portfolio website using HTML5, CSS3, and JavaScript, showcasing my projects, skills, and professional journey in a single, accessible platform. }
            \resumeItem{Incorporated advanced CSS techniques, including the glassmorphism effect, to create a modern, visually appealing design that enhances user engagement and showcases design proficiency. }
\resumeItem{Implemented responsive design principles and interactive JavaScript elements to ensure a seamless user experience across various devices and browsers.}
\resumeItemListEnd
\vspace{-20pt}

\resumeProjectHeading
          {\textbf{Python-Based KBC Quiz Game } $|$ \emph{Python}}{August 2023}
          \resumeItemListStart
            \resumeItem{Developed a "Kaun Banega Crorepati" (KBC) quiz game in Python, leveraging advanced programming concepts such as conditional logic, loops, and data structures to craft a game with progressive difficulty and a dynamic reward system. }
            \resumeItem{Utilized object-oriented programming to design a robust scoring algorithm and integrated data analysis models for question selection and performance tracking, ensuring a seamless gameplay experience with exception handling. }
\resumeItem{Created an engaging command-line interface (CLI) using Python's built-in libraries for user interaction, featuring game state persistence through file I/O operations for an enriched user engagement and gameplay continuity. }
\resumeItemListEnd
\vspace{-20pt}

  \resumeProjectHeading
          {\textbf{Tea Sample Classification} $|$ \emph{Arduino, EDGE Impulse}}{June 2023}
          \resumeItemListStart
            \resumeItem{Devised a Multi-Channel Gas Sensor which distinguishes among 6 different tea samples(Cardamom Tea, Ginger Tea, Masala Tea, Green Tea, Lemon Tea, Assam Tea). }
            \resumeItem{Used Wio Terminal as micro-controller and Grove–Multichannel Gas Sensor V2 as a Multi-Channel Gas Sensor which detects a variety of gases, besides Carbon monoxide(CO), Nitrogen dioxide(NO2), Ethyl alcohol(C2H5CH), Volatile Organic Compounds(VOC) and etc.}   \resumeItem{Gathered data using Grove–Multichannel Gas Sensor V2 and EDGE Impulse, a low-code, no-code platform, where Sensor Readings were published and data analysis was carried out tests.}
          \resumeItemListEnd 
          \vspace{-13pt}

       
    \resumeSubHeadingListEnd

\vspace{-15pt}





%-----------INVOLVEMENT---------------


\end{document}
